<!--Exercise
Editing the YAML header
The YAML header contains the metadata for your report and includes information like the title, author, and output format. In this exercise, you'll update your report by adding some more detail about who created the report and when it was created.

Instructions
100 XP
Add the author field to the YAML header beneath the title and add your name.
 Add the date field below the author information using the Sys.Date() function. -->
 
 ---
title: "Investment Report"
author: "Add your name"
date: "`r Sys.Date()`"
output: html_document
---

```{r data, include = FALSE}
library(readr)

investment_annual_summary <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/d0251f26117bbcf0ea96ac276555b9003f4f7372/investment_annual_summary.csv")
investment_services_projects <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/78b002735b6f620df7f2767e63b76aaca317bf8d/investment_services_projects.csv")
```


## Datasets 

### Investment Annual Summary

The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each region for each fiscal year, from 2012 to 2018.
```{r}
investment_annual_summary
```

### Investment Services Projects

The `investment_services_projects` dataset provides information about each investment project from the 2012 to 2018 fiscal years. Information listed includes the project name, company name, sector, project status, and investment amounts.
```{r}
investment_services_projects 
```


